Inspecting {glmnet} performances

### 2020-03-11 analysis/inspect-glmnet-models.Rmd
workflowr::wflow_publish("analysis/inspect-glmnet-models.Rmd")

```{r}
models <- benchmark_models_new_penalized_mbo_buffer2[[8]][["results"]][["vi_buffer2"]][["Ridge-CV"]][["models"]]
```

@@

We see a high error on Fold 2 (= Laukiz 2).
The others are also quite high but not "out of bounds".

Because this models used the internal optimization of the lambda sequence (`cv.glmnet`), let's look at the value which was chosen for prediction (parameter `s` which defaults to `s="lambda.1se"`):

```{r}
purrr::map_dbl(models, ~ .x[["learner.model"]][["lambda.1se"]])
```

It seems that the `lambda.1se` value for Fold 4 is way higher than for the other 3 folds.
However, all values seem to be quite high.

@@

Interestingly, the lambda length of fold 1 is not 100 (default) but only 5.

@@

To inspect further, let's refit a {glmnet} model directly on the training data of Fold 1 and inspect what `glmnet::cv.glmnet` estimates for the lambda sequence:

@@

Ok, a value of `0.85` is **very** different to what happened during the CV (4.211054e+08).

@@

Ok, how does this compare to summaries of other observations?

@@

Feature "bf2_PRI_norm" has a quite high value.

@@

```{r}
top_ten_abs <- coef(modf4) %>%
  as.matrix() %>%
  as.data.frame() %>%
  dplyr::rename(coef = `1`) %>%
  dplyr::mutate(feature = rownames(coef(modf4))) %>%
  dplyr::slice(-1) %>%
  dplyr::mutate(coef_abs = abs(coef)) %>%
  dplyr::arrange(desc(coef_abs)) %>%
  dplyr::slice(1:10) %>%
  dplyr::pull(feature)
```

@@

Looks ok.

## Compare arguments of the `do.call` call in the benchmark with the manual one

`args` were saved during a debug call of `mlr::benchmark()`

```{r}
args <- readRDS("args-bm-laukiz2.rda")
target_bm <- args$y
features_bm <- args$x

train_inds_bm <- as.numeric(rownames(features_bm))

all.equal(sort(target_bm), sort(target_f4))

all.equal(sort(train_inds_bm), sort(train_inds_fold4))
```

>>>>

```{r}
models <- benchmark_models_new_penalized_mbo_buffer2[[8]][["results"]][["vi_buffer2"]][["Ridge-MBO"]][["models"]]
```

@@

We see a high error on Fold 4 (= Laukiz 2).
The others are also quite high but not "out of bounds".

@@

Interestingly, the lambda length of model 1 is not 100 (default) but only 5.

@@

To inspect further, let's refit a {glmnet} model directly on the training data of Fold 4 and inspect what `glmnet::cv.glmnet` estimates for the lambda sequence:

@@

@@

Ok, how does this compare to summaries of other observations?
NB: Obs. 500 - 510 were chosen randomly.
The purpose here is to see if something within the predictors for specific observations looks abnormal.

@@

Feature "bf2_PRI_norm" has a quite high value (-95).

@@

```{r}
top_ten_abs <- coef(modf4) %>%
  as.matrix() %>%
  as.data.frame() %>%
  dplyr::rename(coef = `1`) %>%
  dplyr::mutate(feature = rownames(coef(modf4))) %>%
  dplyr::slice(-1) %>%
  dplyr::mutate(coef_abs = abs(coef)) %>%
  dplyr::arrange(desc(coef_abs)) %>%
  dplyr::slice(1:10) %>%
  dplyr::pull(feature)

top_ten_abs
```

@@

Looks ok - they are all within a normal range with respectv to the PDP estimates.
